---
title: Latitude and Longitude Coordinates
---
&nbsp;

Introducing the `library(leaflet)` Use 5 lines of code to make an interactive map (Adapted from Machlis.)^[[5 Visualizations in 5 Minutes](http://www.computerworld.com/article/2893271/business-intelligence/5-data-visualizations-in-5-minutes-each-in-5-lines-or-less-of-r.html). ComputerWorld.com by Sharon Machlis]


## Load Libraries

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(leaflet)
```

## Load Data

2012 Starbucks locations ([data source](https://github.com/libjohn/mapping-with-R/blob/master/data/All_Starbucks_Locations_in_the_US_-_Map.csv))

```{r}
starbucks <- read_csv("data/All_Starbucks_Locations_in_the_US_-_Map.csv")
```

### Subset Data to North Carolina
```{r}
starbucksNC <- starbucks  %>% 
  filter(State == "NC")

starbucksNC
```


## Plot Lat and Lon on a Map

Using the `leaflet` function, plot the latitude and longitude on a basemap.  Latitude is *Y*, Longitude is *X*.

```{r plotmap}
starbucksNC %>% 
  leaflet(width = "100%") %>% 
  addTiles() %>% 
  setView(-78.8310, 35.9867, zoom = 10) %>% 
  addMarkers(lat = ~Latitude, 
             lng = ~Longitude, 
             popup = starbucksNC$Name)
```

