---
title: ggmap -- Latitude and Longitude Coordinates
---

## Load Packages

```{r}
library(tidyverse)
library(ggmap)
```

## Load Data

2012 Starbucks locations ([data source](https://github.com/libjohn/mapping-with-R/blob/master/data/All_Starbucks_Locations_in_the_US_-_Map.csv))

```{r}
starbucks <- read_csv("data/All_Starbucks_Locations_in_the_US_-_Map.csv")
```

### Subset Data to North Carolina

Using the same Starbucks from the previous example...
```{r filter-dataset}
starbucksNC <- starbucks  %>% 
  filter(State == "NC")
```

## ggmap

### Indentify base map and mapping location

Some of the most popular base maps come from the Google Maps source.  Using ggmap, the following map types are available from the Google Maps source ...

- terrain
- satellite
- roadmap
- hybrid

Alternatively, use `help(get_map)` to identify additional map sources and other arguments for `maptype`.  For example...

- Stamen maps: "terrain", "watercolor", and "toner" 
- or a positive integer for cloudmade maps (see ?get_cloudmademap)


## Stamen 

First, frame the map

First, Identify the map frame with the "bounding box" coordinates.  In this case use the Southwest and Northeast corners of the map frame (aka "bounding box".)  Display a basemap using Stamen as the source and the Toner as the maptype.

```{r message=FALSE, warning=FALSE}
mapbox <- c(-80, 35.6, -78.5, 36.25)
piedmont_coffee <- get_map(location = mapbox, source = "stamen", maptype = "toner", zoom = 9)
```


```{r}
ggmap(piedmont_coffee)
```

#### Plot Coffee Shops

ggplot2 syntax comes in handy for creating various map views.


```{r message=FALSE, warning=FALSE}

ggmap(piedmont_coffee) +
  geom_point(data = starbucksNC, 
             aes(x = Longitude, y = Latitude), 
             color = "red", 
             size = 2,
             alpha = 0.7) +
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      rect = element_blank(),
      axis.title.y=element_blank(),
      axis.title.x=element_blank())
```


