---
title: ggmap -- Latitude and Longitude Coordinates
---

## Load Packages

```{r}
library(tidyverse)
library(ggmap)
```

## Load Data

2012 Starbucks locations ([data source](https://github.com/libjohn/mapping-with-R/blob/master/data/All_Starbucks_Locations_in_the_US_-_Map.csv))

```{r}
starbucks <- read_csv("data/All_Starbucks_Locations_in_the_US_-_Map.csv")
```

### Subset Data to North Carolina

Using the same Starbucks from the previous example...
```{r filter-dataset}
starbucksNC <- starbucks  %>% 
  filter(State == "NC")
```

## ggmap

### Indentify base map and mapping location

Some of the most popular base maps come from the Google Maps source.  Using ggmap, the following map types are available from the Google Maps source ...

- terrain
- satellite
- roadmap
- hybrid

Alternatively, use `help(get_map)` to identify additional map sources and other arguments for `maptype`.  For example...

- Stamen maps: "terrain", "watercolor", and "toner" 
- or a positive integer for cloudmade maps (see ?get_cloudmademap)


## Stament 

First, frame the map

Altering the map frame from a square to a rectangle requires knowing the coordinates of the Southwest and Northeast corners of the map frame.  This time, display a different basemap using the the Stamen source and the Toner maptype.

```{r message=FALSE, warning=FALSE}
mapbox <- c(-80, 35.6, -78.5, 36.25)
piedmont_coffee <- get_map(location = mapbox, source = "stamen", maptype = "toner", zoom = 9)
```


```{r}
ggmap(piedmont_coffee)
```

#### Plot Coffee Shops

ggplot2 syntax comes in handy for creating various map views.


```{r message=FALSE, warning=FALSE}

ggmap(piedmont_coffee) +
  geom_point(data = starbucksNC, 
             aes(x = Longitude, y = Latitude), 
             color = "red", 
             size = 2,
             alpha = 0.7) +
  theme(axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      rect = element_blank(),
      axis.title.y=element_blank(),
      axis.title.x=element_blank())
```


