---
title: "Exercise 1 Answers: Georeferencing"
output: html_notebook
---

```{r}
library(tidyverse)
library(sf)
library(leaflet)
library(mapview)
```

## Load Data

```{r}
xy_locations <- read_csv("data/mockaroo_latlon.csv")
```

### Plot XY on the Map

There are at least two methods, using `mapview` to plot XY coordinates on a map.  In the blank code-chunks, below, write code to demonstrate at least one of those methods.  Use the `4269` coordinate reference system.

In the example below I use the _S4 Method for XY_ (in case you want to consult the documentation.  https://r-spatial.github.io/mapview/reference/mapView.html )

```{r makemap1}
mapview(xy_locations, xcol = "Longitude", ycol = "Latitude", crs = 4269, grid = FALSE)
```

Write code to demonstrate the other method demonstrated in 01_georeference.html

Below, I will first use the `sf` package to convert a tibble to an _sf tibble_.

```{r alt-makemap}
xy_sf <- st_as_sf(xy_locations, coords = c("Longitude", "Latitude"),  crs=4326)
mapview(xy_sf)
```

## High Contrast & Save

1. Create a high contrast (black and white) map.  
1. Save the file as a .jpeg file.

```{r}
mymap <- mapview(xy_sf, 
                 map.types = "Stamen.Toner", 
                 legend = FALSE,
                 col.regions = "yellow",
                 color = "red",
                 alpha.regions = 1,
                 lwd = 3)
mapshot(mymap, file = "mymap.jpeg")
mymap
```


