---
title: "Exercise 2: Choropleths with tidycensus"
---

## Load Libraries
```{r}
library(tidyverse)
library(tidycensus)
library(sf)
library(leaflet)
library(mapview)
```

## Set API key

Insert your own API Key.  You may request a free key from the Census API tool https://api.census.gov/data/key_signup.html

```{r}
census_api_key("long-string-of-numbers-from-census-api-key-generator")
```


## Choose a census variable

I recommend using one of the following variables.  However, you can use the `tidycensus::load_variables()` and follow the "Searching for variables" [instructions](https://walkerke.github.io/tidycensus/articles/basic-usage.html#searching-for-variables). 

- `B19013_001` - median household income
- `B08131_001`	- AGGREGATE TRAVEL TIME TO WORK (IN MINUTES) OF WORKERS BY PLACE OF WORK--STATE AND COUNTY LEVEL: Worked in State of residence: Workers 16 years and over who did not work at home -- (Estimate)
- `B08103_001` - MEDIAN AGE BY MEANS OF TRANSPORTATION TO WORK: Total: Taxicab, motorcycle, bicycle, or other means: Workers 16 years and over -- (Estimate)


## get_acs()

Load the variable and assign and object name for some USA county using the `get_acs` function.

```{r}
census_variable <- 
  get_acs(geography = "",
          variables = "",
          state = "",
          geometry = TRUE)

```


## Make choropleth 

Make choropleth via `mapview` by filling county polygons (census geography) with correlated value (from the ACS)


```{r make_choropleth}

```


